---
title: "Introduction to the LCZ4r Local Functions"
author: "Max Anjos"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
    html_document:
    toc: true
    toc_float: false
    toc_depth: 2
    number_sections: false
    highlight: "textmate"
    css: custom.css
vignette: >
  %\VignetteIndexEntry{Introduction to the LCZ4r Local Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r , include = FALSE}
knitr::knit_hooks$set(pngquant = knitr::hook_pngquant)
knitr::opts_chunk$set(
  message = FALSE,
  collapse = TRUE,
  comment = "#>",
  dev = "ragg_png",
  dpi = 72,
  fig.retina = 2,
   fig.width = 7,
  fig.height = 6,
  fig.align = "center",
  out.width = "100%",
  pngquant = "--speed=1 --quality=50"
)
```

The **Local functions of LCZ4r**  are designed to operate with more extensive data inputs, such as air temperature readings.

## Getting Started

The **Local functions of `LCZ4r`**, each serving a unique purpose:

| Function             | Description                                | Data Required | Internet Access Required |
|---------------|--------------------------|---------------|---------------|
| `lcz_ts()`           | Analyze LCZ Time Series                    | Not needed    | Not needed               |
| `lcz_anamoly()`      | Calculate LCZ Thermal Anomalies              | Not needed    | Not needed               |
| `lcz_anamoly_map()`      | Visualize LCZ Thermal Anomalies map              | Not needed    | Not needed               |
| `lcz_krige_map()` | Perform LCZ Interpolation with Kriging     | Not needed    | Not needed               |
| `lcz_krige_eval()`   | Evaluate LCZ Interpolation with Kriging    | Not needed    | Not needed               |
| `lcz_idw_map()`   | Perform LCZ Interpolation with IDW         | Not needed    | Not needed               |
| `lcz_idw_eval()`     | Evaluate LCZ Interpolation with IDW        | Not needed    | Not needed               |
| `lcz_uhi()`          | Assess LCZ for Urban Heat Island Intensity | Not needed    | Not needed               |


## Data input
```{r, eval=FALSE}
library(LCZ4r)

#Load data from LCZ4r package
data("lcz_data")

#Check data structure out
str(lcz_data)

```


## Analyze LCZ Time Series


```{r, eval=FALSE}

#Let's get LCZ air temperature time series
lcz_ts(my_map, data_frame = lcz_data, 
       var = "airT", station_id = "station",
       time.freq = "hour", year = 2019:2020)

```

## Calculate LCZ Thermal Anomalies


```{r include=FALSE}
# Let's get LCZ air temperature anomalies in 2019
lcz_anomaly(my_map, data_frame = lcz_data, 
            var = "airT", station_id = "station", 
            time.freq = "hour", year = 2019)

```

## Perform and Evaluate LCZ Interpolation with Kriging


```{r, eval=TRUE}


```

## Perform and Evaluate LCZ Interpolation with IDW


```{r, eval=TRUE}


```

## Assess LCZ for Urban Heat Island Intensit


```{r, eval=TRUE}


```




