---
title: "Introduction to LCZ4r"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
urlcolor: blue
vignette: >
  %\VignetteIndexEntry{Introduction to `LCZ4r`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE,
  out.width = "100%"
)

```

This vignette introduces the **`LCZ4r`** package.

As part of Zoom City Carbon Model (ZCCM), we present the **LCZ4r**, a set of R functions which models Urban Heat Island at high-definition using Local Climate Zone classification and local air temperature readings. 

Please note that **LCZ4r** is currently undergoing develop, and caution is advised when interpreting its outcomes. 

Happy coding!

## Install 

To install LCZ4r, use the development version with latest features

```{r, setup, include=TRUE}

library(LCZ4r)

```


## Overview of the package

The **LCZ4r** package includes 5 functions:

|    Function	   |    description   |     Use of data   | Use of Internet |
|------------------|-------------|-------------------|---------|
| lcz_get_map()       | Get you LCZ map        | Not    | Yes  |
| lcz_plot_map()	     |  Plot you LCZ map      | Not     | Not |
| lcz_cal_area()	     | Calculate LCZ area      | Not    | Not |
| lcz_get_parameters()	   | Get LCZ parameters    | Not    | Not |
| lcz_plot_parameters()	   | Plot LCZ parameters   | Not    | Not |


## Basic Usage

This function gets LCZ for a specified region of interest (ROI) using global LCZ mapping.

```{r, include=TRUE}

#Get your city LCZ map
lcz_map <- lcz_get_map(city="Rio de Janeiro")

#Plot it
lcz_plot_map(lcz_map)

```


This nice function gets all LCZ parameters (including, min, max, and mean) from Stewart and Oke (2012) and converts them to shapefile or raster stack.


|    Code	   |    parameter   |     description   | unit |
|------------------|-------------|-------------------|---------|
| SVF1	       | Sky View Factor        | Minimum Sky View Factor |[0-1] |
| SVF2     | Sky View Factor      | Maximum Sky View Factor |[0-1] |
| SVF3	     | Sky View Factor      | Mean Sky View Factor |[0-1] |

```{r, include=TRUE}

LCZpar <- lcz_get_parameters(lcz_map, istack = TRUE)

lcz_plot_parameters(LCZpar, iselect = "SVF1")

```


This function calculates the LCZ area like this:

```{r, include=TRUE}

LCZarea <- lcz_cal_area(lcz_map, iplot = TRUE)

LCZarea

```







