---
title: "LCZ4r Local Functions"
author: "Max Anjos"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
    rmarkdown::html_vignette:
    toc: true
    toc_float: TRUE
    toc_depth: 2
    number_sections: false
    highlight: "textmate"
    css: custom.css
vignette: >
  %\VignetteIndexEntry{LCZ4r Local Functions}
  %\VignetteEngine{rmarkdown::render}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The **Local functions of LCZ4r** are tailored to handle larger-scale data inputs, such as datasets containing air temperature readings. In this tutorial, we focus on the city of Berlin as our reference location. Specifically, we utilize data collected from 23 meteorological stations situated across the city, which provide hourly time series of air temperature readings. These datasets are sourced from the Urban Climate Observatory (UCO).

## Getting Started

The **Local functions of `LCZ4r`**, each serving a unique purpose:

| Function             | Description                                | Data Required | Internet Access Required |
|---------------|--------------------------|---------------|---------------|
| `lcz_ts()`           | Analyze LCZ Time Series                    | Yes   | Optional*               |
| `lcz_anamoly()`      | Calculate LCZ Thermal Anomalies              | Yes    | Optional               |
| `lcz_anamoly_map()`      | Map LCZ Thermal Anomalies              | Yes    | Optional              |
| `lcz_interp_map()` | Perform LCZ Interpolation     | Yes    | Optional              |
| `lcz_plot_interp()`   | Visualize LCZ Interpolation   | Yes    | Optional               |
| `lcz_uhi_intensity()`          | Assess LCZ for Urban Heat Island Intensity | Yes    | Optional               |
*Optional if you use the `lcz_get_map2()` function.

Tips: 1. Utilize the help(lcz_*) function to access comprehensive documentation for each LCZ function. For instance, you can explore details about the lcz_ts function by typing help("lcz_ts"); 2. Each of these functions includes imputation for missing values within the data.frame. Refer to the documentation of each function and check the "impute" argument for further details on how missing values are handled.


## Data inputs

For the local functions to operate smoothly, you should import the air temperature (or any other environmental variable) into R as a data frame, with columns structured as follows:

1. *date*: This column should contain date-time information. This column must labeled "date".
2. *Station*: Designate a column for meteorological station identifiers.
3. *Air Temperature*: At least one column representing the air temperature variable.
4. *Latitude* and *Longitude*: Two columns are required to specify the geographical coordinates.

It's important to note that the users should standardize the date-time format to R's conventions, such as "2023-03-13 11:00:00" or "2023-03-13". It also includes: e.g. “1/2/1999” or in format i.e. “YYYY-mm-dd”, “1999-02-01”.

To convert from day-month-year to year-month-day:

```{r include=TRUE}

#Note that date column is in the my_data.

#my_data$date <- as.POSIXct(my_data$date, format = "%d-%m-%Y")
#my_data$date <- as.POSIXct(my_data$date, format = "%d-%m-%Y %H:%M:%S")

```


To streamline this process, LCZ4r offers a sample data frame, accessible through the following way:

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(LCZ4r)

#Load data from LCZ4r package
data("lcz_data")

#Check data structure out
str(lcz_data)

```

## Analyze LCZ Time Series

With the `lcz_ts()` function, you can analyze the air temperature associated with LCZ classes over time. For instance, you can perform hourly frequency analysis of air temperature in Berlin for the years 2019-2020 using the "lcz_data" from the LCZ4r package.  

```{r echo=TRUE, fig.height=7, fig.width=11, message=FALSE, warning=FALSE}
# Get the LCZ map for your city
lcz_map <- lcz_get_map_euro(city="Berlin")

#Let's get LCZ air temperature time series
lcz_ts(lcz_map, 
       data_frame = lcz_data, 
       var = "airT", 
       station_id = "station",
       time.freq = "month") # Monthly temporal frequency. Let's change to "hour, "day", "week", and so on.

```

 Additionally, you can customize this function:

**1. Flexibility time selection**
You have the flexibility to select specific years and months for analysis. For example, you can specify a range of years (e.g., 1998:2004) or individual years (e.g., c(1998, 2004)). Similarly, you can select months either numerically (e.g., 1:6 for January to June) or by name (e.g., c("January", "December")). To illustrate, you can select data for September 1st, 2019, by including the arguments "year", "month", and "day" in the function call. See the [utility functions from the openair package](https://bookdown.org/david_carslaw/openair/sections/utilities/utility-functions.html#sec-selectByDate) for more details.    

```{r echo=TRUE, fig.height=7, fig.width=11, message=FALSE, warning=FALSE}

#Selecting one specifique day
lcz_ts(lcz_map, data_frame = lcz_data, 
       var = "airT", station_id = "station",
       time.freq = "hour", 
       year = 2019, month = 9, day = 1)

```

**2. Splitting LCZ time series by temporal window or site**
You can split data frame  calling the *by* argument. The split available are “year”, “season”, “seasonyear”, “month”, “monthyear”, “weekday”, “weekend”, “daylight” (daytime and nighttime). See argument [type in openair package:](https://bookdown.org/david_carslaw/openair/sections/intro/openair-package.html#the-type-option)

## Calculate LCZ Thermal Anomalies

The thermal anomaly is a great way to evaluate the intra-urban air temperatures differences. At each LCZ station, the thermal anomaly is defined as the difference between its temperature and the overall mean temperature of all LCZ stations. For instance, a positive temperature anomaly indicates that a particular LCZ is warmer compared to all other LCZs. The `lcz_anomaly()` function has the same utilities of the `lcz_ts()` regarding **Flexibility time selection** and **Splitting LCZ time series by temporal window or site**.

```{r echo=TRUE, fig.height=7, fig.width=11, message=FALSE, warning=FALSE}

# If you want the thermal anomalies
lcz_anomaly(lcz_map, 
            data_frame = lcz_data, 
            var = "airT", 
            station_id = "station", 
            time.freq = "hour", #Let's change the frequency to "day", "month", "year"
            year = 2019, month = 2, day = 6, hour=5)
```


## Visualize LCZ Thermal Anomaly map

If you're still with us and everything is running rightly, you can proceed to generate a map of LCZ thermal anomalies using the `lcz_anomaly_map()` function. This function employs interpolation techniques such as Kriging ato calculate and interpolate anomalies. The settings for time frequency and data splitting, as utilized in the `lcz_ts` and `lcz_anomaly()` functions, remain relatively unchanged. But, there are two new arguments to consider: **sp.res** (the spatial resolution of the map in meters) and **tp.res** (the frequency at which values are averaged). The `lcz_anomaly_map` function returns either a single raster file or a stack of raster files. Subsequently, you can visualize the anomaly map using the `lcz_plot_interp()` function.

```{r echo=TRUE, fig.height=7, fig.width=11, message=FALSE, warning=FALSE}

#Mapping anomalies for 1st Sep 2020 at 09:00h using kriging
my_anomaly_map <- lcz_anomaly_map(lcz_map,
                                data_frame = lcz_data, 
                                var = "airT", station_id = "station",
                                sp.res = 100, tp.res = "hour",
                                year = 2020, month = 9, day = 1, hour = 9
                                )

#Plot anomaly map. Note that the argument ... is used to title etc..
lcz_plot_interp(my_anomaly_map, 
                title = "LCZ-thermal anomalies", 
                subtitle = "Berlin - 01.09.2020 at 09:00",
                caption = "Source: LCZ4r, 2024.",
                fill = "[ºC]")
```



```{r echo=TRUE, fig.height=7, fig.width=11, message=FALSE, warning=FALSE}

# Active the by argument! Mapping daytime and nighttime anomalies for 1st Sep 2020
my_anomlay_daylight <- lcz_anomaly_map(lcz_map,
                              data_frame = lcz_data, 
                              var = "airT", 
                              station_id = "station",
                              sp.res = 100, 
                              tp.res = "hour",
                              year = 2020, month = 9, day = 1,
                              by="daylight")

my_anomlay_daylight

#Plot anomaly map. Note that I renamed the raster layers
names(my_anomlay_daylight) <- c("daytime", "nighttime")

lcz_plot_interp(my_anomlay_daylight, 
                title = "LCZ-thermal anomalies", 
                subtitle = "Berlin - daytime and nighttime (01.09.2020)",
                caption = "Source: LCZ4r, 2024.",
                fill = "AirT [ºC]")
```


## Perform LCZ Interpolation 

Let's interpolate air temperature using the `lcz_interp_map()`, that follows the logic of the `lcz_anomaly_map()`.

```{r echo=TRUE, fig.height=7, fig.width=11, message=FALSE, warning=FALSE}

air_map <- lcz_interp_map(lcz_map,
                          data_frame = lcz_data,
                          var = "airT",
                          station_id = "station",
                          sp.res = 100,
                          tp.res = "hour",
                          year = 2019, month = 2, day=6, hour=5,
                          LCZinterp = TRUE)
lcz_plot_interp(air_map)

```


## Assess LCZ for Urban Heat Island Intensity

The `lcz_uhi_intensity()` function is designed to calculate the Urban Heat Island (UHI) intensity based on air temperature measurements and Local Climate Zones (LCZ). It provides two methods to calculate UHI intensity (UHII): LCZ and manual. In the LCZ method, the functions automatically identifies the LCZ build types, starting from LCZ 1 and progressing to LCZ 8, to represent the LCZxurban area, whilst it starts from LCZ natural (B, C, D) to LCZ 9 to represent the LCZyrural area. In the manual method  users have the freedom to select stations as references for the urban and rural areas.

```{r, eval=TRUE, fig.height=5, fig.width=9, message=FALSE, warning=FALSE}

#Calculate the hourly UHI intensity for 2019-2020 in Berlin using the LCZ method 
lcz_uhi_intensity(lcz_map,
                  data_frame = lcz_data,
                  var = "airT",
                  station_id = "station",
                  time.freq  = "hour",
                  method = "LCZ",
                  year = 2019:2020)
```


```{r eval=TRUE, fig.height=5, fig.width=9, message=FALSE, warning=FALSE}
#Calculate the hourly UHI intensity for 2020 in Berlin using the manual method
lcz_uhi_intensity(lcz_map,
                  data_frame = lcz_data,
                  var = "airT",
                  station_id = "station",
                  time.freq  = "hour",
                  method = "manual",
                  Turban = "bamberger",
                  Trural = "buch",
                  year = 2020)

```


```{r eval=TRUE, fig.height=5, fig.width=9, message=FALSE, warning=FALSE}
#Calculate the hourly daytime and nighttime of UHI intensity for 6, Feb 2019 in Berlin  
lcz_uhi_intensity(lcz_map,
                  data_frame = lcz_data,
                  var = "airT",
                  station_id = "station",
                  time.freq  = "hour",
                  method = "LCZ",
                  group = TRUE,
                  year = 2019, month= 2, day = 6,
                  by = "daylight")

```


```{r eval=TRUE, fig.height=7, fig.width=11, message=FALSE, warning=FALSE}
#Calculate the hourly daytime and nighttime of UHI intensity by months of 2019 in Berlin  
lcz_uhi_intensity(lcz_map,
                  data_frame = lcz_data,
                  var = "airT",
                  station_id = "station",
                  time.freq  = "hour",
                  method = "LCZ",
                  group = TRUE,
                  year = 2019,
                  by = c("daylight", "month"))

```

