---
title: "Introduction to the Local Functions of LCZ4r"
author: "Max Anjos"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_document:
    toc: true
    toc_float: false
    toc_depth: 2
    number_sections: false
    highlight: "textmate"
    css: custom.css
vignette: >
  %\VignetteIndexEntry{Introduction to the Local Functions of LCZ4r}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r , include = FALSE}
knitr::knit_hooks$set(pngquant = knitr::hook_pngquant)
knitr::opts_chunk$set(
  message = FALSE,
  collapse = TRUE,
  comment = "#>",
  dev = "ragg_png",
  dpi = 72,
  fig.retina = 2,
   fig.width = 7,
  fig.height = 5,
  fig.align = "center",
  out.width = "100%",
  pngquant = "--speed=1 --quality=50"
)
```

This vignette serves as an introduction to the **Local functions of LCZ4r** package. The local functions are designed to operate with more extensive data inputs, such as urban meteorological network readings, including air temperature.

## Getting Started

The **Local functions of `LCZ4r`**, each serving a unique purpose:

| Function             | Description                                | Data Required | Internet Access Required |
|---------------|--------------------------|---------------|---------------|
| `lcz_ts()`           | Analyze LCZ Time Series                    | Not needed    | Not needed               |
| `lcz_anamoly()`      | Explore LCZ Thermal Anomalies              | Not needed    | Not needed               |
| `lcz_interp_krige()` | Perform LCZ Interpolation with Kriging     | Not needed    | Not needed               |
| `lcz_eval_krige()`   | Evaluate LCZ Interpolation with Kriging    | Not needed    | Not needed               |
| `lcz_interp_idw()`   | Perform LCZ Interpolation with IDW         | Not needed    | Not needed               |
| `lcz_eval_idw()`     | Evaluate LCZ Interpolation with IDW        | Not needed    | Not needed               |
| `lcz_uhi()`          | Assess LCZ for Urban Heat Island Intensity | Not needed    | Not needed               |

Happy coding, and enjoy exploring the LCZ4r package!

## Analyze LCZ Time Series

```{r, eval=FALSE}
library(LCZ4r)
```

## Explore LCZ Thermal Anomalies

...

```{r, eval=TRUE}



```

## Perform and Evaluate LCZ Interpolation with Kriging

...

```{r, eval=TRUE}

```

## Perform and Evaluate LCZ Interpolation with IDW

...

```{r, eval=TRUE}

```

## Assess LCZ for Urban Heat Island Intensit

...

```{r, eval=TRUE}

```
